Efficiently stable presentations from error-correcting codes

### 2023-10-02 efficient_stability.tex
finished edits to section 5

@@

    \item \textbf{(Anti-)commutation test:} Sample $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ uniformly at random. Let $\omega = (E_\code e_{i_X}, E_\code e_{i_Z})$ and $\gamma =  (E_\code e_{i_X}) \cdot(E_\code e_{i_Z}) \in \field$. 
		\begin{enumerate} 
		\item If $\gamma=0$ then sample a pair of questions $(x_c,y_c)$ as in the commutation game. Send $(x_c,\omega)$ to $\alice$ and $(y_c,\omega)$ to Bob. Accept if and only if their answers are accepted in the commutation game. 
		\item If $\gamma\neq 0$ then do the same but for the anti-commutation game. 
		\end{enumerate} 
		 \item \textbf{Consistency test:} Sample $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ and $W\in \{X,Z\}$ uniformly at random. Let $\omega=(E_\code e_{i_X}, E_\code e_{i_Z})$ and $\gamma = (E_\code e_{i_X}) \cdot(E_\code e_{i_Z}) \in \field$. Send $(W,\var,i_W)$ to $\alice$ and $(x_{W,\gamma},\omega)$ to $\bob$, where $x_{W,\gamma}$ is a question from the anti-commutation game. Receive $a\in \field$ and $b\in \field$ respectively. Accept if and only if $a=b$. 
    \end{enumerate}
  \end{gamespec}
  \caption{The braiding test over $\code$ verifies that the players respond consistently with a uniformly random codeword from $\code$. $E_\code \in \F_2^{k\times n}$ is a generating matrix for $\code$, and for $i\in\{1,\ldots,n\}$ we let $e_i$ be the $i$-th canonical basis vector of $\F_2^n$.}
  \label{fig:braiding-test}
\end{figure}

Let $\code$ be an $[n,k,d]_2$ linear code and $M=(h,\nu)$ an $r$-local tester for $\code$. We let $E_\code\in\F_2^{k\times n}$ be a generating matrix for $\code$, i.e.\ $E_\code$ is such that its rows are linearly independent and span the codespace. 
 The braiding test constructed from $\code$ and $M$ is described in Figure~\ref{fig:braiding-test}. Informally, the test combines two independent copies of the code game from Section~\ref{sec:code-game} with appropriate commutation and anti-commutation games that will force any successful strategy in the game to be close, in some sense, to a representation of the Pauli group generated by observables $\sigma^X(a)$ and $\sigma^Z(b)$, $a,b\in \F_2^k$ (recall the notation from~\eqref{eq:def-pauli-2}). This is shown in the following theorem.

\begin{theorem}\label{thm:braiding}
Let $\mC$ be a class of tracial von Neumann algebras. Let $\code$ be an $[n,k,d]$ linear code and $M=(h,\nu)$ an $r$-local tester for $\code$. Suppose that the presentation $G(h)$ in~\eqref{eq:def-gh-pres} is such that $G(h)=\Z_2^k$ and furthermore $G(h)$ is $(\delta,\mC)$ sound. Then the braiding test over $\code$ is a $(k,\delta')$-qubit test with sets $S_X=S_Z=\{E_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, map $\phi(W,E_\code e_i)=(W,\eq,i)$ and error function $\delta' = O(\delta^{1/2}(6\eps))$.\footnote{Assume $E_\code$ has no repeated columns.} 
\end{theorem}

@@

\begin{proof}
This follows by expending the left-hand side and using $\tau(P_aQ_{a'})\geq 0$ for all $a\neq a'$. 
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:braiding}]
\underline{Completeness:} We first verify completeness. For $W\in\{X,Z\}$, $i\in\{1,\ldots,n\}$ and $b\in \F_2$ let $P^{(W,\eq,i)}_b = \frac{1}{2}(\Id + (-1)^b\sigma^W(E_\code e_i))$, and for $a\in \F_2^S$ let $P^{(W,\var,j)}_a = \prod_{i: h_{ji}=1} P^{(W,\eq,i)}_{a_i}$. Writing $(f_0,f_1)$ for the canonical basis of $\C^2$, $P^{(W,\var,j)}_a$ is the projection on the span of all $\otimes_{i=1}^k f_{u_i}$ where $u=(u_1,\ldots,u_k)$ is such that $u^T E_\code=a$.   
For $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ let $\omega=(E_\code e_{i_X}, E_\code e_{i_Z})$ and $\gamma =(E_\code e_{i_X}) \cdot(E_\code e_{i_Z}) $. We let $P^{x_{W,\gamma},\omega} = P^{(W,\var,i_W)}$.

These choices already ensure that the strategy succeeds with probability $1$ in the consistency test. We verify that it succeeds in the code test. Let $j\in\{1,\ldots,k\}$. As observed above, for any $a\in\field^r$ such that $P^{W,\eq,j}_a\neq 0$ there is an $u\in \field^k$ such that $u^TE_\code=a$, which means that $a\in \code$. 
% and $h\in \F_2^S$ any valid parity check, i.e.\ $h^T E_\code=0$, for $\code$ with support in $S$. Then $\sum_{i\in S} h_i E_\code e_i = 0$, so $\prod_{i\in S}(\sigma^W(E_\code e_i))^{h_i}=\Id$. This means that for any $a\in\field^S$ such that $P^{W,S}_a\neq 0$, we have that $h\cdot a =0$, i.e.\ $a$ satisfies the parity check 
Using the completeness property of $M$ it follows that $M$ must accept any $a$ such that $P^{W,\eq,j}_a\neq 0$, which shows that the strategy succeeds in the code test with probability $1$.

It remains to verify that the anti-commutation test is passed with probability $1$. For this we observe that 
% To define $P^{(x_c,\omega)}$ and $P^{(x_a,\omega)}$ for $x_c\notin \{x_{Z,0},x_{Z,0}\}$ and $x_a \notin \{x_{X,1},x_{Z,1}\}$ we observe that 
the binary observables 
\[ U=\widehat{ P}^{x_{X,\gamma},\omega} \quad\text{and}\quad V= \widehat{P}^{x_{Z,\gamma},\omega} \]
commute in case $\gamma=0$ and anti-commute in case $\gamma=1$. This is because by construction $U=\sigma^X(E_\code i_X)$ and $V=\sigma^W(E_\code i_W)$, and because of the definition of $\gamma$. Hence the pair $(U,V)$ can be completed to a perfect strategy for the commutation game (if $\gamma=0)$ or anti-commutation game (if $\gamma=1)$. This defines the measurements $P^{(x,\omega)}$ for $x\notin \{x_{W,\gamma},W\in\{X,Z\},\gamma\in\{0,1\}\}$.

@@

\underline{Soundness:} Next we show soundness. Let $\strategy$ be a synchronous strategy for the braiding test  in  $(\mM,\tau)$ that succeeds with probability at least $1-\eps$. For $W\in\{X,Z\}$ let $\strategy^W$ be the strategy in $G_{\code,M}$ that is obtained by restricting $\strategy$ to the relevant measurements corresponding to the ``Code test'' part of the braiding test, i.e.\ the $P^{W,\eq,j}$ and $P^{W,\var,i}$.  Then $\strategy^W$ succeeds with probability at least $1-3\eps$ in $G_{\code,M}$. Using Proposition~\ref{prop:rep-game} it follows that $\{\widehat{P}^{W,\var,i}\}$ is an $O(\eps)$-homomorphism of $G(h)$. Under the assumption that $G(h)=\Z_2^k$ is $(\delta,\mC)$-stable, we deduce that there is a $\delta_1 = O({\delta(6\eps)})$ such that for each $W\in\{X,Z\}$, $\strategy^W$ is $(\delta_1,\nu)$ close to a perfect strategy $\tilde{\strategy}^W$ on $(\mN^W,\tau^W)$ for $G_{\code,M}$, where $\nu$ is uniform on $\{1,\ldots,n\}$. This strategy has measurement operators $\{ \tilde{P}^{W,\eq,j}_a\}$ and $\{\tilde{P}^{W,\var,i}_b\}$ which satisfy 
\begin{equation}\label{eq:main-0}
\Es{i\in\{1,\ldots,n\}}\sum_{b \in \F_2} \big\|P^{W,\eq,i}_b - (w^W)^* \tilde{P}_b^{W,\eq,i} w^W \big\|^2_2 \,=\, O(\delta_1)\;.
\end{equation}
Furthermore, using that $G(h)=\Z_2^k$ is Abelian, there is a  POVM $\{\tilde{P}^W_u\}_{u\in \field^n}$ such that $\sum_{u\in \code}\tilde{P}^W_u = \Id$ and for each $i\in \{1,\ldots,n\}$, $\tilde{P}^{W,i}_b = \sum_{u:u_i=b} \tilde{P}^W_u$.

Applying Lemma~\ref{lem:pull-back}, we obtain projective measurements $\{Q^W_u\}$ on $\mM$ such that 
\begin{equation}\label{eq:main-1}
\sum_u \big\|Q^W_u - (w^W)^* \tilde{P}_u^W w^W \big\|^2_2 \,=\, O(\delta_1)\;.
\end{equation}
For any $i\in\{1,\ldots,n\}$ let $Q^{W,i}_b = \sum_{a:\,a_i=b}  Q^W_a$. Then by Lemma~\ref{lem:dp},
\begin{align*}
\Es{i}\sum_b \tau\big( Q^{W,i}_b (w^W)^*\tilde{P}^{W,i}_b(w^W) \big)
&\geq \Es{i}\sum_a \tau\big( Q^{W}_a (w^W)^*\tilde{P}^{W}_a(w^W) \big)\\
&\geq 1-O(\delta_1)\;.
\end{align*}
For $W\in\{X,Z\}$ and $b\in \F_2^k$ let $R^W_b = Q^W_{G_\mC^T b}$, where by definition $G_\mC^T b\in \mC$.

@@

It remains to verify that $\strategy'$ succeeds in the game $G_{\dlS}$ with probability $1-O(\sqrt{\delta_1})$. By definition $\strategy'$ succeeds in the (anti)-commutation test with probability $1-O(\eps)$. It remains to check the $W$-consistency test, for $W\in\{X,Z\}$. Because $\strategy$ succeeds with probability $1-O(\eps)$ in the consistency test, 
\begin{equation*}
\Es{i_X,i_Z\in\{1,\ldots,n\}} \sum_b \tau\big( P^{W,i}_b P^{x_{W,\gamma},\omega}_b\big) \,\geq\, 1-O(\eps)\;,\
\end{equation*}
where $\omega$ and $\gamma$ are defined as in Figure~\ref{fig:braiding-test}. Using~\eqref{eq:main-0},~\eqref{eq:main-1}
and Lemma~\ref{lem:close-value} it follows that 
\begin{equation*}
\Es{i_X,i_Z\in\{1,\ldots,n\}} \sum_b \tau\big( Q^{W,i}_b P^{x_{W,\gamma},\omega}_b\big) \,\geq\, 1-O(\sqrt{\delta_1})\;,\
\end{equation*}
Using~\eqref{eq:main-3}, this can be rewritten as 
\begin{equation}\label{eq:main-4}
\Es{i_X,i_Z\in\{1,\ldots,n\}} \sum_{b,c: (G_\mC^T c)_i=b} \tau\big( R^{W}_c P^{x_{W,\gamma},\omega}_b\big) \,\geq\, 1-O(\sqrt{\delta_1})\;.
\end{equation}
Since $\omega_W = G_\mC e_i$, $(G_\mC^T c)_i = c\cdot \omega_W$. Thus~\eqref{eq:main-4} shows that $\strategy'$ succeeds with probability $1-O(\sqrt{\delta_1})$ in the $W$-consistency test, as desired. 
\end{proof}

\subsection{The Pauli braiding test}
\label{sec:pbt}

By instantiating $\code$ using the Reed-Muller code from Section~\ref{sec:eff-z2k} we obtain an efficient entanglement test.  Because we do not know if $G(h_\bRM)$ is Abelian, we need to introduce an additional test for the relations $\{R_k^\com\}$ in~\eqref{eq:z2k-eff}. The resulting test is described in Figure~\ref{fig:pbt}.

\begin{figure}[!htbp]
  \centering
  \begin{gamespec}
Let $h_\bRM\in \F_2^{M\times N}$ be the parity check matrix for $\code_\bRM$ considered in Section~\ref{sec:eff-z2k}. Here, $N=q^{m+1}$ and $M=q^{m+2}(1+m)$. Let $\mu_R$ be the distribution on relations~\eqref{eq:z2k-eff} described in Section~\ref{sec:eff-z2k}. Execute either of the following tests with probability $1/4$ each. 
    \begin{enumerate}
      \setlength\itemsep{1pt}
    \item \textbf{Code test:} Identical to that in Figure~\ref{fig:braiding-test}.
    \item \textbf{(Anti-)commutation test:} Identical to that in Figure~\ref{fig:braiding-test}.
		 \item \textbf{Consistency test:} Identical to that in Figure~\ref{fig:braiding-test}.
		\item \textbf{Pairwise commutation test:} Sample $(i,i')\in \{1,\ldots,N\}^2$ according to the distribution $\mu_R$, conditioned on choosing a relation from $R_k^\com$. and $W\in \{X,Z\}$ uniformly at random. 	
		Let $\omega=(E_\code e_{i}, E_\code e_{i'})$ an 
		Sample a pair of questions $(x_c,y_c)$ as in the commutation game. If either question is $x_{X,0}$ or $x_{Z,0}$, replace it with $(W,\var,i)$ or $(W,\var,i')$ respectively. Otherwise, send the original question together with $\omega$, i.e.\ $(x_c,\omega)$ or $(y_c,\omega)$ respectively. Accept if and only if the players' answers are accepted in the commutation game.  
    \end{enumerate}
  \end{gamespec}
  \caption{The Pauli braiding test, obtained by adapting the braiding test from Figure~\ref{fig:braiding-test} to the $[q^{m+1},t(d+1)^m,D']_2$ code $\code_\bRM$.}
  \label{fig:pbt}

@@

\begin{proof}
Let $\strategy$ be a synchronous strategy that succeeds in the braiding test with probability at least $1-\eps$. Then in particular the strategy succeeds with probability at least $1-4\eps/3$ in the braiding test over $\bRM$. Since $(\code_\bRM,M)$ is not known to be abelian, we cannot apply Theorem~\ref{thm:braiding} directly. However, we can follow its proof.

@@

For the soundness part, we first define the same pair of strategies $\strategy^X$ and $\strategy^Z$ for $G_{\code_\bRM,M}$. Applying Proposition~\ref{prop:rep-game}, we deduce an $O(d\eps)$-homomorphism of the presentation~\eqref{eq:def-gh-pres} of $G(h_\bRM)$. However, we are interested in constructing an approximate homomorphism of the presentation~\eqref{eq:z2k-eff}, which in addition contains the relations $R_k^\com$. The fact that $x_i \mapsto \widehat{P}^{(W,\var,i)}$ satisfies these relations, on average and according to the distribution $\mu_R$, follows from success in the pairwise commutation test executed as part of the Pauli braiding test (Figure~\ref{fig:pbt}). Thus we obtain that $x_i \mapsto \widehat{P}^{(W,\var,i)}$ is an $(O(d\eps),\mu_R)$-homomorphism of the presentation~\eqref{eq:z2k-eff}. Applying Theorem~\ref{thm:z2-stab}, and similarly to the proof of Theorem~\ref{thm:braiding} we obtain a pair of POVMs $\{\tilde{P}^W_u\}_{u\in\F_2^N}$, for $W\in\{X,Z\}$, such that defining $\tilde{P}^{W,i}_b = \sum_{u:u_i=b} \tilde{P}^W_u$ these operators satisfy~\eqref{eq:main-0}, with right-hand side $\delta_2 = \delta(O(d\eps))$, with $\delta$ the soundness function from Theorem~\ref{thm:z2-stab}. From here on the proof proceeds exactly as Theorem~\ref{thm:braiding}, leading to the desired conclusion. 
\end{proof}

>>>>

An $r$-local linear tester $M=(h,\nu)$ for $\code$ induces a pair of distributions $(\nu_R,\nu_S)$ on the relations and generators of the presentation $G(h)$\eqref{eq:def-gh-pres} in a natural way: For the generators, we let $\nu_S$ be induced from $\nu$ by first sampling $j\sim \nu$ and then a uniformly random $i$ such that $h_{ji}\neq 0$. For the relations, we let $\nu_R$ be the uniform mixture of the distribution $\nu_S$ on relations $x_j^2=e$, the distribution $\nu$ on relations $R_i$, and the distribution $\nu\times \nu_S\times \nu_S$ on relations $R'_{jii'}$.

@@

    \item \textbf{(Anti-)commutation test:} Sample $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ uniformly at random. Let $\omega = (E_\code e_{i_X}, E_\code e_{i_Z})$ and $\gamma =  (E_\code e_{i_X}) \cdot(E_\code e_{i_Z}) \in \field$. 
		\begin{enumerate} 
		\item If $\gamma=0$ then sample a pair of questions $(x_c,y_c)\sim\mu_\cc$ as in the commutation game. Send $(x_c,\omega)$ to $\alice$ and $(y_c,\omega)$ to Bob. Accept if and only if their answers are accepted in the commutation game. 
		\item If $\gamma\neq 0$ then do the same but for the anti-commutation game. 
		\end{enumerate} 
		 \item \textbf{Consistency test:} Sample $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ and $W\in \{X,Z\}$ uniformly at random. Let $\omega=(E_\code e_{i_X}, E_\code e_{i_Z})$ and $\gamma = (E_\code e_{i_X}) \cdot(E_\code e_{i_Z}) \in \field$. Send $(W,\var,i_W)$ to $\alice$ and $(x_{W,\gamma},\omega)$ to $\bob$, where $x_{W,\gamma}$ is a question from the (anti-)commutation game. Receive $a\in \field$ and $b\in \field$ respectively. Accept if and only if $a=b$. 
    \end{enumerate}
  \end{gamespec}
  \caption{The braiding test over $\code$ verifies that the players respond consistently with a uniformly random codeword from $\code$. $E_\code \in \F_2^{k\times n}$ is a generating matrix for $\code$, and for $i\in\{1,\ldots,n\}$ we let $e_i$ be the $i$-th canonical basis vector of $\F_2^n$.}
  \label{fig:braiding-test}
\end{figure}

Let $\code$ be an $[n,k,d]_2$ linear code and $M=(h,\nu)$ an $r$-local tester for $\code$. We let $E_\code\in\F_2^{k\times n}$ be a generating matrix for $\code$, i.e.\ $E_\code$ is such that its rows are linearly independent and span the codespace. 
 The braiding test constructed from $\code$ and $M$ is a synchronous game described in Figure~\ref{fig:braiding-test}. The test combines two independent copies of the code game from Section~\ref{sec:code-game} with appropriate commutation and anti-commutation sub-tests. The braiding test is designed to force any successful strategy in it to be close, in some sense, to a representation of the Pauli group generated by observables $\sigma^X(a)$ and $\sigma^Z(b)$, $a,b\in \F_2^k$ (recall the notation from~\eqref{eq:def-pauli-2}). This is shown in the following theorem.

\begin{theorem}\label{thm:braiding}
Let $\mC$ be a class of tracial von Neumann algebras. Let $\code$ be an $[n,k,d]_2$ linear code and $M=(h,\nu)$ an $r$-local tester for $\code$. Suppose that the presentation $G(h)$ in~\eqref{eq:def-gh-pres} is such that $G(h)=\Z_2^k$ and furthermore this presentation is $(\delta,\nu_R,\nu_S,\mC)$-stable.\footnote{The distributions $\nu_R$ and $\nu_S$ are defined from $\nu$ as described right after Definition~\ref{def:code-test}.} Then the braiding test over $\code$ is a $(k,\delta')$-qubit test with sets $S_X=S_Z=\{E_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, map $\phi(W,E_\code e_i)=(W,\eq,i)$ and error function $\delta' = O(\delta^{1/2}(6\eps))$.\footnote{Assume $E_\code$ has no repeated columns.} 
\end{theorem}

@@

\begin{proof}
This follows by expanding the left-hand side and using $\tau(P_aQ_{a'})\geq 0$ for all $a\neq a'$. 
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:braiding}]
\underline{Completeness:} We first verify completeness. For $W\in\{X,Z\}$, $i\in\{1,\ldots,n\}$ and $b\in \F_2$ let $P^{(W,\var,i)}_b = \frac{1}{2}(\Id + (-1)^b\sigma^W(E_\code e_i))$, and for $j\in\{1,\ldots,m\}$, with $m$ the number of rows of $h$, and $a\in \F_2^r$ let $P^{(W,\eq,j)}_a = \prod_{i: h_{ji}=1} P^{(W,\var,i)}_{a_i}$. Writing $(f_0,f_1)$ for the canonical basis of $\C^2$, $P^{(W,\eq,j)}_a$ is the projection on the span of all $\otimes_{i=1}^k f_{u_i}$ where $u=(u_1,\ldots,u_k)$ is such that $(u^T E_\code)_{|S_j}=a$, where $S_j$ denotes the support of $h_{j\cdot}$.   
For $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ let $\omega=(E_\code e_{i_X}, E_\code e_{i_Z})$ and $\gamma =(E_\code e_{i_X}) \cdot(E_\code e_{i_Z}) $. We let $P^{x_{W,\gamma},\omega} = P^{(W,\var,i_W)}$.

These choices already ensure that the strategy succeeds with probability $1$ in the consistency test. We verify that it succeeds in the code test. Let $j\in\{1,\ldots,m\}$. As observed above, for any $a\in\field^r$ such that $P^{W,\eq,j}_a\neq 0$ there is an $u\in \field^k$ such that $(u^TE_\code)_{|S_j}=a$, which means that $a$ is the restriction of a valid element of $\code$. 
% and $h\in \F_2^S$ any valid parity check, i.e.\ $h^T E_\code=0$, for $\code$ with support in $S$. Then $\sum_{i\in S} h_i E_\code e_i = 0$, so $\prod_{i\in S}(\sigma^W(E_\code e_i))^{h_i}=\Id$. This means that for any $a\in\field^S$ such that $P^{W,S}_a\neq 0$, we have that $h\cdot a =0$, i.e.\ $a$ satisfies the parity check 
Using the completeness property of $M$ it follows that $M$ must accept any $a$ such that $P^{W,\eq,j}_a\neq 0$, which shows that the strategy succeeds in the code test with probability $1$.

It remains to verify that the anti-commutation test is passed with probability $1$. For this we observe that 
% To define $P^{(x_c,\omega)}$ and $P^{(x_a,\omega)}$ for $x_c\notin \{x_{Z,0},x_{Z,0}\}$ and $x_a \notin \{x_{X,1},x_{Z,1}\}$ we observe that 
the binary observables 
\[ U=\widehat{ P}^{x_{X,\gamma},\omega} \quad\text{and}\quad V= \widehat{P}^{x_{Z,\gamma},\omega} \]
commute in case $\gamma=0$ and anti-commute in case $\gamma=1$. This is because by construction $U=\sigma^X(E_\code i_X)$ and $V=\sigma^W(E_\code i_W)$, and because of the definition of $\gamma$. Hence the pair $(U,V)$ can be completed to a perfect strategy for the commutation game (if $\gamma=0)$ or anti-commutation game (if $\gamma=1)$. This defines the measurements $P^{(x,\omega)}$ for $x\notin \{x_{W,\gamma}:\,W\in\{X,Z\},\gamma\in\{0,1\}\}$.

@@

\underline{Soundness:} Next we show soundness. Let $\strategy$ be a synchronous strategy for the braiding test  in  $(\mM,\tau)$ that succeeds with probability at least $1-\eps$. For $W\in\{X,Z\}$ let $\strategy^W$ be the strategy in $G_{\code,M}$ that is obtained by restricting $\strategy$ to the relevant measurements corresponding to the ``Code test'' part of the braiding test, i.e.\ the $P^{W,\eq,j}$ and $P^{W,\var,i}$.  Then $\strategy^W$ succeeds with probability at least $1-6\eps$ in $G_{\code,M}$. Using Proposition~\ref{prop:rep-game} it follows that $\{\widehat{P}^{W,\var,i}\}$ is an $O(\eps)$-homomorphism of $G(h)$. Under the assumption that $G(h)=\Z_2^k$ is $(\delta,\nu_R,\nu_S,\mC)$-stable, we deduce that there is a $\delta_1 = O({\delta(6\eps)})$ such that for each $W\in\{X,Z\}$, $\strategy^W$ is $(\delta_1,\nu)$-close to a perfect strategy $\tilde{\strategy}^W$ on $(\mN^W,\tau^W)$ for $G_{\code,M}$, where $\nu$ is uniform on $\{1,\ldots,n\}$. This strategy has measurement operators $\{ \tilde{P}^{W,\eq,j}_a\}$ and $\{\tilde{P}^{W,\var,i}_b\}$ which satisfy 
\begin{equation}\label{eq:main-0}
\Es{i\in\{1,\ldots,n\}}\sum_{b \in \F_2} \big\|P^{W,\var,i}_b - (w^W)^* \tilde{P}_b^{W,\var,i} w^W \big\|^2_2 \,=\, O(\delta_1)\;.
\end{equation}
Furthermore, using that $G(h)=\Z_2^k$ is Abelian, there is a  POVM $\{\tilde{P}^W_u\}_{u\in \field^n}$ such that $\sum_{u\in \code}\tilde{P}^W_u = \Id$ and for each $i\in \{1,\ldots,n\}$, $\tilde{P}^{W,i}_b = \sum_{u:u_i=b} \tilde{P}^W_u$.

Applying Lemma~\ref{lem:pull-back}, we obtain projective measurements $\{Q^W_u\}$ on $\mM$ such that 
\begin{equation}\label{eq:main-1}
\sum_u \big\|Q^W_u - (w^W)^* \tilde{P}_u^W w^W \big\|^2_2 \,=\, O(\delta_1)\;.
\end{equation}
For any $i\in\{1,\ldots,n\}$ let $Q^{W,i}_b = \sum_{u:\,u_i=b}  Q^W_u$. Then by Lemma~\ref{lem:dp},
\begin{align*}
\Es{i}\sum_b \tau\big( Q^{W,i}_b (w^W)^*\tilde{P}^{W,i}_b(w^W) \big)
&\geq \Es{i}\sum_u \tau\big( Q^{W}_u (w^W)^*\tilde{P}^{W}_u(w^W) \big)\\
&\geq 1-O(\delta_1)\;.
\end{align*}
For $W\in\{X,Z\}$ and $b\in \F_2^k$ let $R^W_b = Q^W_{G_\mC^T b}$, where by definition $G_\mC^T b\in \mC$.

@@

It remains to verify that $\strategy'$ succeeds in the game $G_{\dlS}$ with probability $1-O(\sqrt{\delta_1})$. By definition $\strategy'$ succeeds in the (anti)-commutation test with probability $1-O(\eps)$. It remains to check the $W$-consistency test, for $W\in\{X,Z\}$. Because $\strategy$ succeeds with probability $1-O(\eps)$ in the consistency test, 
\begin{equation*}
\Es{i_X,i_Z\in\{1,\ldots,n\}} \sum_b \tau\big( P^{W,\var,i}_b P^{x_{W,\gamma},\omega}_b\big) \,\geq\, 1-O(\eps)\;,\
\end{equation*}
where $\omega$ and $\gamma$ are defined as in Figure~\ref{fig:braiding-test}. Using~\eqref{eq:main-0},~\eqref{eq:main-1}
and Lemma~\ref{lem:close-value} it follows that 
\begin{equation*}
\Es{i_X,i_Z\in\{1,\ldots,n\}} \sum_b \tau\big( Q^{W,i}_b P^{x_{W,\gamma},\omega}_b\big) \,\geq\, 1-O(\sqrt{\delta_1})\;,\
\end{equation*}
Using~\eqref{eq:main-3}, this can be rewritten as 
\begin{equation}\label{eq:main-4}
\Es{i_X,i_Z\in\{1,\ldots,n\}} \sum_{b,c: (G_\mC^T c)_i=b} \tau\big( R^{W}_c P^{x_{W,\gamma},\omega}_b\big) \,\geq\, 1-O(\sqrt{\delta_1})\;.
\end{equation}
Since $\omega_W = G_\mC e_i$, $(G_\mC^T c)_i = c\cdot \omega_W$. Thus~\eqref{eq:main-4} shows that $\strategy'$ succeeds with probability $1-O(\sqrt{\delta_1})$ in the $W$-consistency test, as desired. 
\end{proof}

\subsection{The quantum low-degree test}
\label{sec:pbt}

By instantiating $\code$ using the Reed-Muller code from Section~\ref{sec:eff-z2k} we obtain an efficient qubit test.  Because we do not know if $G(h_\bRM)$ is Abelian, we need to introduce an additional test for the relations $\{R_k^\com\}$ in~\eqref{eq:z2k-eff}. The resulting test is described in Figure~\ref{fig:pbt}. It is a variant of a test first introduced in~\cite{natarajan2018low} (with a flawed analysis). This paper (together with the work on which our analysis relies) corrects this. In the next section we detail an important application of this test in the work~\ref{ji2020mip}.

\begin{figure}[!htbp]
  \centering
  \begin{gamespec}
Let $h_\bRM\in \F_2^{M\times N}$ be the parity check matrix for $\code_\bRM$ considered in Section~\ref{sec:eff-z2k}. Here, $N=q^{m+1}$ and $M=q^{m+2}(1+m)$. Let $\mu_R$ be the distribution on relations~\eqref{eq:z2k-eff} described in Section~\ref{sec:eff-z2k}. Execute either of the following tests with probability $1/4$ each. 
    \begin{enumerate}
      \setlength\itemsep{1pt}
    \item \textbf{Code test:} Identical to that in Figure~\ref{fig:braiding-test}.
    \item \textbf{(Anti-)commutation test:} Identical to that in Figure~\ref{fig:braiding-test}.
		 \item \textbf{Consistency test:} Identical to that in Figure~\ref{fig:braiding-test}.
		\item \textbf{Pairwise commutation test:} Sample $(i,i')\in \{1,\ldots,N\}^2$ according to the distribution $\mu_R$, conditioned on choosing a relation from $R_k^\com$, and $W\in \{X,Z\}$ uniformly at random. 	
		Let $\omega=(E_\code e_{i}, E_\code e_{i'})$. 
		Sample a pair of questions $(x_c,y_c)$ as in the commutation game. If either question is $x_{X,0}$ or $x_{Z,0}$, replace it with $(W,\var,i)$ or $(W,\var,i')$ respectively. Otherwise, send the original question together with $\omega$, i.e.\ $(x_c,\omega)$ or $(y_c,\omega)$ respectively. Accept if and only if the players' answers are accepted in the commutation game.  
    \end{enumerate}
  \end{gamespec}
  \caption{The quantum low-degree test, obtained by adapting the braiding test from Figure~\ref{fig:braiding-test} to the $[q^{m+1},t(d+1)^m,D']_2$ code $\code_\bRM$.}
  \label{fig:pbt}

@@

\begin{proof}
Let $\strategy$ be a synchronous strategy that succeeds in the braiding test with probability at least $1-\eps$. Then in particular the strategy succeeds with probability at least $1-4\eps/3$ in the braiding test over $\code_\bRM$. Since $(\code_\bRM,M)$ is not known to be abelian, we cannot apply Theorem~\ref{thm:braiding} directly. However, we can follow its proof.

@@

For the soundness part, we first define the same pair of strategies $\strategy^X$ and $\strategy^Z$ for $G_{\code_\bRM,M}$. Applying Proposition~\ref{prop:rep-game}, we deduce an $O(d\eps)$-homomorphism of the presentation~\eqref{eq:def-gh-pres} of $G(h_\bRM)$. However, we are interested in constructing an approximate homomorphism of the presentation~\eqref{eq:z2k-eff}, which in addition contains the relations $R_k^\com$. The fact that $x_i \mapsto \widehat{P}^{(W,\var,i)}$ satisfies these relations, on average and according to the distribution $\mu_R$, follows from success in the pairwise commutation test executed as part of the Pauli braiding test (Figure~\ref{fig:pbt}). Thus we obtain that $x_i \mapsto \widehat{P}^{(W,\var,i)}$ is an $(O(d\eps),\mu_R)$-homomorphism of the presentation~\eqref{eq:z2k-eff}. Applying Theorem~\ref{thm:z2-stab}, and similarly to the proof of Theorem~\ref{thm:braiding} we obtain a pair of POVMs $\{\tilde{P}^W_u\}_{u\in\F_2^N}$, for $W\in\{X,Z\}$, such that defining $\tilde{P}^{W,i}_b = \sum_{u:u_i=b} \tilde{P}^W_u$ these operators satisfy~\eqref{eq:main-0}, with right-hand side $\delta_2 = \delta(O(d\eps))$, with $\delta$ the soundness function from Theorem~\ref{thm:z2-stab}. From here on the proof proceeds exactly as the proof of Theorem~\ref{thm:braiding}. 
\end{proof}
